Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-09-02 main.Rmd
Better section numbers/titles

## Circular {#sec:circular-gran-def}

@@

## Quasi-circular {#sec:quasi-circular-gran-def}

@@

## Aperiodic {#sec:aperiodic-gran-def}

@@

### Single-to-multiple {#sec:single-to-multiple}

@@

### Multiple-to-single {#sec:multiple-to-single}

@@

#### Multiple order-up quasi-circular granularities {#sec:quasi-circular-multiple}

@@

# Data structure{#sec:data-structure}

@@

### Cyclic granularities search and computation:

>>>>

## Circular granularities {#sec:circular-gran-def}

@@

## Quasi-circular granularities {#sec:quasi-circular-gran-def}

@@

## Aperiodic granularities {#sec:aperiodic-gran-def}

@@

### Single-to-multiple order-up {-}

@@

### Multiple-to-single order-up {-}

@@

### Multiple order-up quasi-circular granularities {-}

@@

# Data structure {#sec:data-structure}

@@

### Cyclic granularities search and computation {-}
